Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization

### 2019-03-27 WRITEUP/ms.tex
revisions and comments on Sect 3 Numerical Methods

@@

The simulation zooms in on a galaxy named
%mm 
   after the flower 
\flower whose properties are given in 
%mm \citet{Pallottini17b} 
      \citet{Pallottini17a} 
and are briefly summarized in the following. \flower is a Lyman-break galaxy 
%mm (LBG), [unused acronym]
that at $z\simeq 6$ is hosted by a dark matter halo of mass $M_{\rm DM}\simeq$\,10$^{11}$\,\Msun at the center of a cosmic web knot, and accretes mass from the IGM mainly via three filaments of length $\simeq$\,100\,kpc. \flower has a stellar mass of $M_\star\simeq$\,3\E{10}\,\Msun, a metallicity of $Z\simeq$\,0.5\,$Z_{\odot}$, a molecular gas mass of $M_{\rm H2}\simeq$\,5\E{7}\,\Msun, and a SFR of $\simeq$\,100\,\Msun\,yr\pmOne. \MM{What is its gas fraction?  I ask because its molecular gas mass is minuscule, particularly for such a high SFR: this is a depletion time of only 0.5 Myr, while modern galaxies usually have depletion times more like 0.5--2~Gyr!} Its effective stellar radius  is $\sim$0.5\,kpc and the dark matter virial radius is $r_{\rm 200}\simeq$\,15\,kpc.

@@

The \SF history\footnote{Note that here the SFR is calculated based on the stellar mass formed in the last 10 Myr within 3.5 kpc from the galaxy center of mass. The SFR plotted in Figure 2 of \citet{Pallottini17b} is a factor of two higher since there the SFR account for the contribution from massive satellite galaxies within the virial radius ($\approx$15\,kpc).} of \flower is shown in \Fig{SFH}. The SFR of \flower varies between $\sim$30$-$80\,\Msun\,yr\pmOne as it evolves from an actively accreting phase to a starburst phase after a merger, and then back to a relatively quiescent phase, over the simulated $\approx 700$ Myr.

Given \flower's SF stochastic nature, in this work we mostly focus on the analysis of two of its most extreme evolutionary stages (see \Sec{singless}). The two phases correspond to (a) intense accretion (b) starburst (\Fig{SFH}). We are interesting in determining whether MCC properties are sensitive to these different dynamical conditions. For completeness, for the other evolutionary stages traced in the simulation we only show scaling relations (see \Fig{alpha16-28}).

Throughout this paper, we dub as ``satellite galaxies'' the dense gas regions outside the main disk of \flower. The distinction between clumps and satellites is admittedly somewhat ambiguous, and we consider it only as a working one.
\AF{To be discussed at the end}

>>>>

%\def\altomega{r_{\rm disk}}
\def\altomega{\varpi}

@@

The simulation zooms in on a galaxy named
%mm 
   after the flower 
\flower whose properties are given in 
%mm \citet{Pallottini17b} 
      \citet{Pallottini17a} 
and are briefly summarized in the following. \flower is a Lyman-break galaxy 
%mm (LBG), [unused acronym]
that at $z\simeq 6$ is hosted by a dark matter halo of mass $M_{\rm
  DM}\simeq$\,10$^{11}$\,\Msun at the center of a cosmic web knot, and
accretes mass from the IGM mainly via three filaments of length
$\simeq$\,100\,kpc. \flower has a stellar mass of
$M_\star\simeq$\,3\E{10}\,\Msun, a metallicity of
$Z\simeq$\,0.5\,$Z_{\odot}$, a molecular gas mass of $M_{\rm
  H2}\simeq$\,5\E{7}\,\Msun, and a SFR of $\simeq$\,
%mm [not according to Figure 1] 100
     50--70
\,\Msun\,yr\pmOne. \MM{What is its gas fraction?  I ask because its
  molecular gas mass is minuscule, particularly for such a high SFR:
  this is a depletion time of only 0.7--1 Myr, while modern galaxies
  usually have depletion times more like 0.5--2~{\em Gyr!}} Its effective stellar radius  is $\sim$0.5\,kpc and the dark matter virial radius is $r_{\rm 200}\simeq$\,15\,kpc.

@@

The \SF history\footnote{Note that here the SFR is calculated based on the stellar mass formed in the last 10 Myr within 3.5 kpc from the galaxy center of mass. The SFR plotted in Figure 2 of \citet{Pallottini17b} is a factor of two higher since there the SFR accounts for the contribution from massive satellite galaxies within the virial radius ($\approx$15\,kpc).} of \flower is shown in \Fig{SFH}. The SFR of \flower varies between $\sim$30$-$80\,\Msun\,yr\pmOne as it evolves from an actively accreting phase to a starburst phase after a merger, and then back to a relatively quiescent phase, over the simulated $\approx 700$ Myr.

Given \flower's SF stochastic nature, in this work we mostly focus on
the analysis of two of its most extreme evolutionary stages (see
\Sec{singless}). The two phases correspond to (a) intense accretion
(b) starburst (\Fig{SFH}). We are interesting in determining whether
MCC properties are sensitive to these different dynamical
conditions. For completeness, for the other evolutionary stages traced
in the simulation we only show scaling relations (see 
%mm [Figures must be numbered and placed in order cited.  Better to
%cite to the section and leave the figure in its proper place.] \Fig{alpha16-28}).
     Sect.~\ref{sec:ncut}).

Throughout this paper, we 
%mm dub as ``satellite galaxies'' the dense gas regions outside the
%main disk of \flower. 
     describe  the dense gas regions outside the main disk of \flower
     as satellite galaxies.
The distinction between clumps and satellites is admittedly somewhat
ambiguous, though, and we consider it only as a working one.
\AF{To be discussed at the end}
